A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-21 paper.tex
merge error

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c}
 $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[sect:2d44minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$} & \\ \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{dR}})$} & \\  \hline
 \multirow{6}*{$(2,2)$} & \multirow{2}*{\hyperref[sect:2d22minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$} & \\  \cline{2-4}
  & \multirow{2}*{\hyperref[sect:2d22Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to $R$ matter} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d22Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{dR}})$} & \\  \hline
 \multirow{2}*{$(\mc N_+, 0)$} & \multirow{2}*{\hyperref[sect:2dN0minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_+ - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$} & \\  \hline
 \multirow{2}*{$(4,0)$} & \multirow{2}*{\hyperref[sect:2d40minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Sect}(\CC, (U \otimes K_\CC^{1/2}) \ham \gg)$} & \\  \hline
 \multirow{2}*{$(2,0)$} & \multirow{2}*{\hyperref[sect:2d20minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, R/\gg)$} & \\ \hline
 \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.  When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$. When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.  We can promote the supersymmetry to $\mc N=(8,8)$ when $U = T^*\gg$, but no new twists occur.}
 \label{table_of_twists_2d}
\end{table}

@@

\subsubsection{Rank \texorpdfstring{$(1, 2)$}{(1,2)} Topological Twist}

Next we look at the case of the twist by a rank $(1,2)$ supercharge. 
As in many cases so far, it will be useful to consider a family of supercharges which are generically of rank $(1,2)$.

We use the same twisting homomorphism $\phi\colon \MU(2) \to \Spin(6;\CC)$ and twisting datum $\alpha\colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
\[
S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \oplus \det(L)^{-1}.
\]
The representation $S_- \otimes W^*$ decomposes as
\[
S_- \otimes W^* = L \oplus L^* \oplus \CC Q'\oplus\eend_0(L),
\]
where $\eend_0(L)\subset \eend(L)$ is the subspace of traceless endomorphisms. The supercharge $Q_0$ has rank $(1, 0)$ and the supercharge $Q'$ has rank $(0, 2)$. Moreover, both are square-zero and commute with each other. Therefore, we may consider a family of square-zero supercharges
\begin{equation}
Q_t = Q_0 + tQ'
\label{eq:4d412Hodgefamily}
\end{equation}
which is of rank $(1, 0)$ at $t=0$ and of rank $(1, 2)$ at $t\neq 0$.

We are going to use the notation of the fields from Section \ref{sect:4d4holomorphictwist}.

\begin{prop}
Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}. The $\MU(2)$ decomposition of the functionals $I^{(1)}, I^{(2)}$ (see \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}) in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
\begin{align*}
I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varsigma, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varsigma^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varsigma^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
\end{align*}
\end{prop}

@@

\section{Dimension 2}
The odd part of the $2$-dimensional supersymmetry algebra is 
\[
\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_- .
\]
The complex semi-spin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.

@@

\begin{theorem} \label{thm:2d(N,0)}
The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$.
This equivalence is $\U(1)$-equivariant.
\end{theorem}

>>>>

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c}
 $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[sect:2d44minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$} & \\ \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{dR}})$} & \\  \hline
 \multirow{6}*{$(2,2)$} & \multirow{2}*{\hyperref[sect:2d22minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$} & \\  \cline{2-4}
  & \multirow{2}*{\hyperref[sect:2d22Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to $R$ matter} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d22Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{dR}})$} & \\  \hline
 \multirow{2}*{$(\mc N_+, 0)$} & \multirow{2}*{\hyperref[sect:2dN0minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_+ - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$} & \\  \hline
 \multirow{2}*{$(4,0)$} & \multirow{2}*{\hyperref[sect:2d40minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Sect}(\CC, (U \otimes K_\CC^{1/2}) \ham \gg)$} & \\  \hline
 \multirow{2}*{$(2,0)$} & \multirow{2}*{\hyperref[sect:2d20minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, R/\gg)$} & \\ \hline
 \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.  When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$. When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.  We can promote the supersymmetry to $\mc N=(8,8)$ when $U = T^*\gg$, but no new twists occur.}
 \label{table_of_twists_2d}
\end{table}

@@

\subsubsection{Rank \texorpdfstring{$(2,1)$}{(1,2)} Topological Twist}

%Next we look at the case of the twist by a rank $(1,2)$ supercharge. 
%As in many cases so far, it will be useful to consider a family of supercharges which are generically of rank $(1,2)$. 
%
%We use the same twisting homomorphism $\phi\colon \MU(2) \to \Spin(6;\CC)$ and twisting datum $\alpha\colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
%Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
%\[
%S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \oplus \det(L)^{-1}.
%\]
%The representation $S_- \otimes W^*$ decomposes as
%\[
%S_- \otimes W^* = L \oplus L^* \oplus \CC Q'\oplus\eend_0(L),
%\]
%where $\eend_0(L)\subset \eend(L)$ is the subspace of traceless endomorphisms. The supercharge $Q_0$ has rank $(1, 0)$ and the supercharge $Q'$ has rank $(0, 2)$. Moreover, both are square-zero and commute with each other. Therefore, we may consider a family of square-zero supercharges
%\begin{equation}
%Q_t = Q_0 + tQ'
%\label{eq:4d412Hodgefamily}
%\end{equation}
%which is of rank $(1, 0)$ at $t=0$ and of rank $(1, 2)$ at $t\neq 0$.
%
%We are going to use the notation of the fields from Section \ref{sect:4d4holomorphictwist}.
%
%\begin{prop}
%Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}. The $\MU(2)$ decomposition of the functionals $I^{(1)}, I^{(2)}$ (see \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}) in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
%\begin{align*}
%I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varsigma, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varsigma^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
%&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varsigma^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
%I^{(2)} (Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
%\end{align*}
%\end{prop}

@@

\section{Dimension 2}
The odd part of the $2$-dimensional supersymmetry algebra is 
\[
\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_- .
\]
The complex semi-spin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality, where $\Spin(2;\CC)$ acts on $\CC_1, \CC_{-1}$ with weights $1, -1$ respectively.

@@

\begin{theorem} \label{thm:2d(N,0)}
The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
This equivalence is $\U(1)$-equivariant.
\end{theorem}
